### 2012-11-14 paper/isca40format/Variations.tex
stuff

The protocol given above satisfies all the constraints \ref{} to \ref{}, except,
potentially, Constraint \ref{orderreq}. Before the upgrade response for address
$a$ sent from $c$ to $c'$ has reached $c'$, $c'$ could have received a downgrade
request sent from the parent. This happens as follows (Figure
\ref{msi-fifo-needed}, with the numbers indicating the order in which the
messages are sent, for outgoing edges, and received for incoming edges). Cache
$c$ sends the upgrade response (and data) to cache $c'$, and its own downgrade
response along with the \FwdAck{} to the directory. The directory receives the
downgrade response from $c$. Soon afterwards, the directory wants to downgrade
the state of $a$ in $c'$ to $I$ (let's say, because some other cache wants to
upgrade its state for $a$ to $M$).  The directory sends a downgrade to $I$
request to $c'$ for address $a$. This downgrade request to $c'$ from the parent
reaches $c'$ before the (forwarded) upgrade response from $c$, violating
Constraint \ref{orderreq}. However, as we saw in Section \ref{sec:nofifoorder},
Constraint \ref{orderreq} can be satisfied by tagging the downgrade request with
the state the directory was in for cache $c'$ and address $a$ right before the
request to $c'$ was sent -- FIFO ordering is not required from the network. $c'$
will not process the downgrade request till it has received the upgrade response
from $c$.

>>>>

The protocol given above satisfies all the constraints \ref{} to \ref{}, except,
potentially, Constraint \ref{orderreq}. Before the upgrade response for address
$a$ sent from $c$ to $c'$ has reached $c'$, $c'$ could have received a downgrade
request sent from the directory. This happens as follows (Figure
\ref{msi-fifo-needed}, with the numbers indicating the order in which the
messages are sent, for outgoing edges, and received for incoming edges). Cache
$c$ sends the upgrade response (and data) to cache $c'$, and its own downgrade
response along with the \FwdAck{} to the directory. The directory receives the
downgrade response from $c$. Soon afterwards, the directory wants to downgrade
the state of $a$ in $c'$ to $I$ (let's say, because some other cache wants to
upgrade its state for $a$ to $M$).  The directory sends a downgrade to $I$
request to $c'$ for address $a$. This downgrade request to $c'$ from the directory
reaches $c'$ before the (forwarded) upgrade response from $c$, violating
Constraint \ref{orderreq}. However, as we saw in Section \ref{sec:nofifoorder},
Constraint \ref{orderreq} can be satisfied by tagging the downgrade request with
the state the directory was in for cache $c'$ and address $a$ right before the
request to $c'$ was sent -- FIFO ordering is not required from the network. $c'$
will not process the downgrade request till it has received the upgrade response
from $c$.
